### 2009-04-02 talk/icooolps2009-dotnet/clibackend.tex
try to make images and listings fit into a column

\begin{figure}[h]
\begin{center}
\includegraphics[height=5cm]{flexswitch1}
\includegraphics[height=5cm]{flexswitch2}
\caption{An example of a flexswitch evolution: in the picture on the
  right a new block has been dynamically added.}\label{flexswitch-fig}
\end{center}
\end{figure}

@@

\subsubsection{Implementation of flexswitches}
Finally, we can have a look at the implementation of flexswitches.
The following snippet shows the special case of integer flexswitches.
\begin{small}
\begin{lstlisting}[language={[Sharp]C}] 
public class IntLowLevelFlexSwitch:BaseLowLevelFlexSwitch {
  public uint default_blockid = 0xFFFFFFFF;
  public int numcases = 0;
  public int[] values = new int[4];
  public FlexSwitchCase[] cases = new FlexSwitchCase[4];

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[height=4.5cm]{flexswitch1}
\includegraphics[height=4.5cm]{flexswitch2}
\caption{An example of a flexswitch evolution: in the picture on the
  right a new block has been dynamically added.}\label{flexswitch-fig}
\end{center}
\end{figure}

@@

\subsubsection{Implementation of flexswitches}
Finally, we can have a look at the implementation of flexswitches.
The following snippet shows the special case of integer flexswitches.
\begin{small}
\begin{lstlisting}[language={[Sharp]C}] 
public class IntLowLevelFlexSwitch: 
                        BaseLowLevelFlexSwitch {
  public uint default_blockid = 0xFFFFFFFF;
  public int numcases = 0;
  public int[] values = new int[4];
  public FlexSwitchCase[] cases = 
                          new FlexSwitchCase[4];
